\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Project Proposal}
\author{Group 2}
\date{October 2023}

\begin{document}

\maketitle

We plan on implementing a model to simulate the occurrence of a pandemic (such as COVID-19) on a cluster of people. Each person will be represented by a point on the x/y plane, where some of them are infected. This simulation will last for a certain time steps. For each time step, every person will move in the area. Then for a healthy person, the probability of getting ill depends on the distance of carriers and other factors; and for an infected person, there are certain probabilities of being healed, maintained or dead. We are planning on storing the info about each person using a person class, and making plots and animation to show the results. \par

The above is our general plan, and we plan on implementing other features to make the model a bit more complex. First, we plan to simulate the types of movement of the crowds, such as random walking, gathering tendency and separating tendency. Besides, we could simulate the epidemic prevention strategies for each person, such as mask wearing, vaccination and self-quarantine. Finally, we may implement a single player game, where the player acts as a healthy person, choosing different strategies to avoid being infected (or acts as virus carrier to infect more people :) ). We will implement other ideas into our simulation depending on time constraints and instructor's feedback. 

\end{document}
